### 2018-08-08 Sections/quantum_repeater_networks.tex
floats
Indexing

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Curvature of Earth}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell pairs}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variable states}.

\begin{figure}[!htb]
\includegraphics[width=0.475\textwidth]{repeaters_1}
\caption{(a) Schematic representation of an entangled Bell pair $| \Psi\rangle_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

We begin our preparation of a long-range entangled link by creating multiple entangled pairs between adjacent repeater nodes (the number will depend both on the quality of the pairs we initially generate and also the target quality we want our final pair to have). Once we have enough pairs established between two repeater nodes, we perform entanglement purification\index{Entanglement purification}, which converts multiple entangled links (pairs) into a fewer number with higher quality. 
\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{repeaters_2}
\caption{Basic operation of a (first generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure} 
These purification steps, shown in Fig.~\ref{fig:repeaters_2}(a-b), are performed on the links between all adjacent repeaters, increasing the quality of the links between those adjacent repeater stations to the required degree. Entanglement swapping, as shown in Fig.~\ref{fig:repeaters_2}(c), then creates links twice as long. The resulting entanglement links can then be used iteratively for further rounds of purification and swapping until one generates a high quality link between the desired points in the network.

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{repeaters_3}
\caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitter}\index{Polarising beamsplitter} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

@@

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{repeaters_4}
\caption{Entanglement purification: (a) The simplest purification scheme involving two pairs of shared remote entangled quantum memories (\mbox{$A_1-B_1$} and \mbox{$A_2-B_2$}). The purification operation begins with Alice performing a CNOT operation between memories $A_1$ and $B_1$. Similarly Bob performs a CNOT operation between his memories. Alice and Bob then measure qubits $A_2$ and $B_2$ in the computational ($0$, $1$) basis and share their results. They discard the resulting state if between them they measured odd parity ($0,1$ or $1,0$). They keep the state if they measured an even parity between them ($0,0$ or $1,1$) which should have higher fidelity. (b) Two qubits are removed, leaving a residual two-qubit state between $A_1$ and $B_1$ with improved fidelity.} 
\label{fig:repeaters_4}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{repeaters_5}
\caption{Plot of the increased fidelity and success probability for entanglement purification for a mixture of two Bell states with initial fidelity $F$. The dashed lines show how multiple pairs with an initial fidelity $F=0.7$ can be purified iteratively to a final fidelity above 0.95.} 
\label{fig:rep_purification}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{repeaters_6}
\caption{Entanglement swapping: (a) An entangled state is shared between Alice and a repeater station ($A_1-A_2$), and also between the repeater station and Bob ($B_2-B_1$). The entanglement operation begins by performing a Bell state measurement between $A_2$ and $B_2$ using a CNOT gate, and measurements at $D_1$, $D_2$.  The measurements indicate which Bell state we have projected our state $A_1$, $B_1$ onto. (b) The resultant entangled state between $A_1$, $B_1$ with the qubits $A_2$ and $B_2$ disentangled from it.}
\label{fig:repeaters_6}
\end{figure}

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{repeaters_7}
\caption{Purification circuit based on quantum error correction. The specific example shown is for the [[5,1,3]] code \cite{bib:Bennettr1996a, bib:Knill97}. We assume that entanglement distribution has allowed Alice and Bob to create 5 copies of their imperfect Bell pairs. The error correction circuit is executed independently between the two nodes. While we show the situation when the measurements at both sides are done directly on four pairs of entangled qubits (leaving us with one unencoded Bell pair), one can also use ancilla qubits to measure the appropriate syndromes. As soon as the measurements are complete both nodes' qubits are available for continued use as the error correction is deterministic and there are no failure events that need to be heralded. In this case the classical message between nodes just carries Alice's measurement results, allowing either node to interpret which Bell state was generated and for one of them to apply the bit-flip or phase-flip correction operation if needed to recover the desired Bell state. In many cases this correction is classically tracked in the Pauli frame, which keeps a record of whether $\hat{X}$ and/or $\hat{Z}$ corrections need to be performed at some stage \cite{bib:jiang09, bib:munro10}. Note that it's not necessary to measure out all but one of the qubits involved in the entangled links. Instead the logical qubit can be maintained by the use of ancilla qubits within that node with the syndrome being measured with the help of the ancilla qubits. Entanglement swapping could then be performed on the logical qubits enabling a much more error resilient system.
}
\label{fig:repeaters_7}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{repeaters_8}
\caption{A butterfly design quantum repeater network protocol that reduces the requirements on all the quantum memory times to only that associated with the signalling time between adjacent repeater nodes \cite{bib:munro10}. Enough pairs must be generated between the node to ensure that we can use them in the error correction code in a single round trip time between adjacent nodes. The scheme relies on multiple entangled pairs being generated temporally, starting from the mid point of the network. The protocol begins with the central node creating links to both the left and right nearest neighbour nodes in sufficient number to allow an error correction code to be implemented. Once they are created the error correction circuits are applied to the links left and right of this central node (effectively creating encoded logical links). Entanglement swapping at the middle node is then applied  between these logical links, creating a logical link between the left and right adjacent nodes. The left and right nodes can then do the same to their next adjacent repeater nodes, error correcting as they go, until the desired end-to-end entangled link is achieved.}
\label{fig:repeaters_8}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=0.8\textwidth]{repeaters_9}
\caption{Transmission of a quantum signal using loss based error correction codes in a quantum network.}
\label{fig:repeaters_9}
\end{figure*}

@@

\startnormtable
\begin{widetext}
\begin{center}
\begin{table}[!htb]
\centering
\begin{tabular}{ccccc}
\hline
\multicolumn{1}{|l|}{\textbf{Repeater generation}} & \multicolumn{1}{l|}{\rm $T_\mathrm{av}$}   & \multicolumn{1}{l|}{\rm Resources consumed}    & \multicolumn{1}{l|}{\rm  $L_\mathrm{max}$}     & \multicolumn{1}{l|}{\rm  Local gate precision}     \\ \hline \hline
\multicolumn{1}{|l|}{First generation}    & \multicolumn{1}{l|}{$O(L_\mathrm{tot}/c)$} & \multicolumn{1}{l|}{$O(\mathrm{poly}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{\rm arbitrary}  & \multicolumn{1}{l|}{\rm arbitrary}    \\ \hline
\multicolumn{1}{|l|}{Second generation}   & \multicolumn{1}{l|}{$O(2 L/c)$}     & \multicolumn{1}{l|}{$O(\mathrm{polylog}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{\rm arbitrary}  & \multicolumn{1}{l|}{\rm high}   \\ \hline
\multicolumn{1}{|l|}{Third generation}   & \multicolumn{1}{l|}{$O(t_\mathrm{local})$}     & \multicolumn{1}{l|}{$O(\mathrm{polylog}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{$L/L_0<0.69$}   & \multicolumn{1}{l|}{\rm fault tolerant levels}   \\
\hline
\end{tabular}
\caption{Quantum repeater approaches and their expected performance scalings.  $T_\mathrm{av}$ corresponds to the time between which the protocol can be attempted (the time to generate a single Bell state is at least $L_\mathrm{tot}/c$) \cite{bib:Muralidharan2016}. The generation rate is $R\sim 1/T_\mathrm{av}$. Further given are the resources (quantum memories) required as well as the precision for the local gate operations within repeater nodes. $L_\mathrm{max}$ is the maximum spacing between repeater nodes. $L_\mathrm{tot}$ is the total distance between Alice and Bob while $L$ is the distance between adjacent repeater nodes. $t_\mathrm{local}$ is the time required to perform the local operations within the repeater node, while $L_0$ is the attenuation length of the channel/fibre.}
\label{tab:rep_nets_scale}
\end{table}
\end{center}
\end{widetext}
\startalgtable

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{racetime}
\caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time condition} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure*}

>>>>

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Curvature of Earth}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell states}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variable states}.

\begin{figure}[htpb]
\includegraphics[width=0.475\textwidth]{repeaters_1}
\caption{(a) Schematic representation of an entangled Bell pair $| \Psi\rangle_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

We begin our preparation of a long-range entangled link by creating multiple entangled pairs between adjacent repeater nodes (the number will depend both on the quality of the pairs we initially generate and also the target quality we want our final pair to have). Once we have enough pairs established between two repeater nodes, we perform entanglement purification\index{Entanglement purification}, which converts multiple entangled links (pairs) into a fewer number with higher quality. 
\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{repeaters_2}
\caption{Basic operation of a (first generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure} 
These purification steps, shown in Fig.~\ref{fig:repeaters_2}(a-b), are performed on the links between all adjacent repeaters, increasing the quality of the links between those adjacent repeater stations to the required degree. Entanglement swapping, as shown in Fig.~\ref{fig:repeaters_2}(c), then creates links twice as long. The resulting entanglement links can then be used iteratively for further rounds of purification and swapping until one generates a high quality link between the desired points in the network.

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[htpb]
\includegraphics[width=0.3\textwidth]{repeaters_3}
\caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitters}\index{Polarising beamsplitter} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

@@

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{repeaters_4}
\caption{Entanglement purification: (a) The simplest purification scheme involving two pairs of shared remote entangled quantum memories (\mbox{$A_1-B_1$} and \mbox{$A_2-B_2$}). The purification operation begins with Alice performing a CNOT operation between memories $A_1$ and $B_1$. Similarly Bob performs a CNOT operation between his memories. Alice and Bob then measure qubits $A_2$ and $B_2$ in the computational ($0$, $1$) basis and share their results. They discard the resulting state if between them they measured odd parity ($0,1$ or $1,0$). They keep the state if they measured an even parity between them ($0,0$ or $1,1$) which should have higher fidelity. (b) Two qubits are removed, leaving a residual two-qubit state between $A_1$ and $B_1$ with improved fidelity.} 
\label{fig:repeaters_4}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{repeaters_5}
\caption{Plot of the increased fidelity and success probability for entanglement purification for a mixture of two Bell states with initial fidelity $F$. The dashed lines show how multiple pairs with an initial fidelity $F=0.7$ can be purified iteratively to a final fidelity above 0.95.} 
\label{fig:rep_purification}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{repeaters_6}
\caption{Entanglement swapping: (a) An entangled state is shared between Alice and a repeater station ($A_1-A_2$), and also between the repeater station and Bob ($B_2-B_1$). The entanglement operation begins by performing a Bell state measurement between $A_2$ and $B_2$ using a CNOT gate, and measurements at $D_1$, $D_2$.  The measurements indicate which Bell state we have projected our state $A_1$, $B_1$ onto. (b) The resultant entangled state between $A_1$, $B_1$ with the qubits $A_2$ and $B_2$ disentangled from it.}
\label{fig:repeaters_6}
\end{figure}

@@

\begin{figure*}[htpb]
\includegraphics[width=\textwidth]{repeaters_7}
\caption{Purification circuit based on quantum error correction. The specific example shown is for the [[5,1,3]] code \cite{bib:Bennettr1996a, bib:Knill97}. We assume that entanglement distribution has allowed Alice and Bob to create 5 copies of their imperfect Bell pairs. The error correction circuit is executed independently between the two nodes. While we show the situation when the measurements at both sides are done directly on four pairs of entangled qubits (leaving us with one unencoded Bell pair), one can also use ancilla qubits to measure the appropriate syndromes. As soon as the measurements are complete both nodes' qubits are available for continued use as the error correction is deterministic and there are no failure events that need to be heralded. In this case the classical message between nodes just carries Alice's measurement results, allowing either node to interpret which Bell state was generated and for one of them to apply the bit-flip or phase-flip correction operation if needed to recover the desired Bell state. In many cases this correction is classically tracked in the Pauli frame, which keeps a record of whether $\hat{X}$ and/or $\hat{Z}$ corrections need to be performed at some stage \cite{bib:jiang09, bib:munro10}. Note that it's not necessary to measure out all but one of the qubits involved in the entangled links. Instead the logical qubit can be maintained by the use of ancilla qubits within that node with the syndrome being measured with the help of the ancilla qubits. Entanglement swapping could then be performed on the logical qubits enabling a much more error resilient system.
}
\label{fig:repeaters_7}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=\textwidth]{repeaters_8}
\caption{A butterfly design quantum repeater network protocol that reduces the requirements on all the quantum memory times to only that associated with the signalling time between adjacent repeater nodes \cite{bib:munro10}. Enough pairs must be generated between the node to ensure that we can use them in the error correction code in a single round trip time between adjacent nodes. The scheme relies on multiple entangled pairs being generated temporally, starting from the mid point of the network. The protocol begins with the central node creating links to both the left and right nearest neighbour nodes in sufficient number to allow an error correction code to be implemented. Once they are created the error correction circuits are applied to the links left and right of this central node (effectively creating encoded logical links). Entanglement swapping at the middle node is then applied  between these logical links, creating a logical link between the left and right adjacent nodes. The left and right nodes can then do the same to their next adjacent repeater nodes, error correcting as they go, until the desired end-to-end entangled link is achieved.}
\label{fig:repeaters_8}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.8\textwidth]{repeaters_9}
\caption{Transmission of a quantum signal using loss based error correction codes in a quantum network.}
\label{fig:repeaters_9}
\end{figure*}

@@

\startnormtable
\begin{widetext}
\begin{center}
\begin{table}[htpb]
\centering
\begin{tabular}{ccccc}
\hline
\multicolumn{1}{|l|}{\textbf{Repeater generation}} & \multicolumn{1}{l|}{\rm $T_\mathrm{av}$}   & \multicolumn{1}{l|}{\rm Resources consumed}    & \multicolumn{1}{l|}{\rm  $L_\mathrm{max}$}     & \multicolumn{1}{l|}{\rm  Local gate precision}     \\ \hline \hline
\multicolumn{1}{|l|}{First generation}    & \multicolumn{1}{l|}{$O(L_\mathrm{tot}/c)$} & \multicolumn{1}{l|}{$O(\mathrm{poly}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{\rm arbitrary}  & \multicolumn{1}{l|}{\rm arbitrary}    \\ \hline
\multicolumn{1}{|l|}{Second generation}   & \multicolumn{1}{l|}{$O(2 L/c)$}     & \multicolumn{1}{l|}{$O(\mathrm{polylog}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{\rm arbitrary}  & \multicolumn{1}{l|}{\rm high}   \\ \hline
\multicolumn{1}{|l|}{Third generation}   & \multicolumn{1}{l|}{$O(t_\mathrm{local})$}     & \multicolumn{1}{l|}{$O(\mathrm{polylog}(L_\mathrm{tot}))$} & \multicolumn{1}{l|}{$L/L_0<0.69$}   & \multicolumn{1}{l|}{\rm fault tolerant levels}   \\
\hline
\end{tabular}
\caption{Quantum repeater approaches and their expected performance scalings.  $T_\mathrm{av}$ corresponds to the time between which the protocol can be attempted (the time to generate a single Bell state is at least $L_\mathrm{tot}/c$) \cite{bib:Muralidharan2016}. The generation rate is $R\sim 1/T_\mathrm{av}$. Further given are the resources (quantum memories) required as well as the precision for the local gate operations within repeater nodes. $L_\mathrm{max}$ is the maximum spacing between repeater nodes. $L_\mathrm{tot}$ is the total distance between Alice and Bob while $L$ is the distance between adjacent repeater nodes. $t_\mathrm{local}$ is the time required to perform the local operations within the repeater node, while $L_0$ is the attenuation length of the channel/fibre.}
\label{tab:rep_nets_scale}
\end{table}
\end{center}
\end{widetext}
\startalgtable

@@

\begin{figure*}[htpb]
\includegraphics[width=\textwidth]{racetime}
\caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time condition} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure*}
